Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Cambiando los his/her por their o they para referirse a users

As a summary, this application includes two modules: a \textit{controller} and an \textit{actuator}. The first one monitors the environment (context) and the user's behaviour, translating his/her actions in a sequence of events. These events, along with the patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module. Then, a decision is taken in the corporate security operations centre (SOC) side, considering the RT2AE output and the set of security rules adapted to that specific user and context. The corresponding feedback is communicated to the user through the \textit{actuator}, which is also in charge of triggering the recommended actions to stop the user's or application's doings, in case it is required.

@@

The rest of the components are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager} which controls the communications between client and server sides. 
In addition, there are two types of applications considered in this system: on the one hand the \textit{MUSES Aware App}, which is an application adapted to MUSES, so the system can directly interact with it (monitoring and acting). This application must be implemented using the MUSES API (Application Program Interface)\footnote{The MUSES API is defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}. On the other hand the \textit{Non MUSES Aware App} is that which MUSES cannot directly interact with. Usually it can be accessed through the operating system (OS). So the type of information to gather from them and also the type of actions to do over them vary depending on the OS. In most of the cases MUSES could just detect/recognize very specific events, and also do very limited actions to prevent or block them (maybe showing a screen on the top until something is accomplished by the user). This is due to the usual forbiddance or limitation of interactions with other applications that the OSs have. %FERGU: forbiddance parece que existe, pero el corrector me dice que no. Prohibition mejor?
% Yo diría que es forbidding...

>>>>

As a summary, this application includes two modules: a \textit{controller} and an \textit{actuator}. The first one monitors the environment (context) and the user's behaviour, translating their actions in a sequence of events. These events, along with the patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module. Then, a decision is taken in the corporate security operations centre (SOC) side, considering the RT2AE output and the set of security rules adapted to that specific user and context. The corresponding feedback is communicated to the user through the \textit{actuator}, which is also in charge of triggering the recommended actions to stop the user's or application's doings, in case it is required.

@@

The rest of the components are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager} which controls the communications between client and server sides. 
In addition, there are two types of applications considered in this system: on the one hand the \textit{MUSES Aware App}, which is an application adapted to MUSES, so the system can directly interact with it (monitoring and acting). This application must be implemented using the MUSES API (Application Program Interface)\footnote{The MUSES API is defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}. On the other hand the \textit{Non MUSES Aware App} is that which MUSES cannot directly interact with. Usually it can be accessed through the operating system (OS). So the type of information to gather from them and also the type of actions to do over them vary depending on the OS. In most of the cases MUSES could just detect/recognize very specific events, and also do very limited actions to prevent or block them (maybe showing a screen on the top until something is accomplished by the user). This is due to the usual denial or limitation of interactions with other applications that the OSs have. %FERGU: forbiddance parece que existe, pero el corrector me dice que no. Prohibition mejor?
% Yo diría que es forbidding...
